---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

devtools::load_all()
```

# roadnetdb

<!-- badges: start -->
<!-- badges: end -->

roadnetdb is package for construction and operation of road networks on a database. 
This package provides functions using pgRouting and OpenStreetMap road data.

> roadnetdbはデータベース上で道路ネットワークを構築・運用するためのパッケージです。
> このパッケージはpgRoutingとOpenStreetMapの道路データを用いた関数を提供します。

## Installation

You can install the development version of roadnetdb like so:

> roadnetdbの開発版は以下のようにインストールできます。

``` r
install.packages("remotes")
remotes::install_git("https://github.com/gitlab/ando/roadnetdb")
```

## Usage

Load the package as follows:

> パッケージを以下のように読み込みます。

```{r example, eval=FALSE}
library(roadnetdb)
```

### Preparing the Database

First, you need to prepare the database.
roadnetdb works with PostgreSQL database.
The package provides a function to launch the database using docker.

> まず、データベースを準備する必要があります。
> roadnetdbでは、PostgreSQLを対象に動作するようになっています。
> このパッケージでは、次の関数を用いてdockerによるデータベースの構築が可能です。

```{r launch_database, eval=FALSE}
launch_database()
```

The function builds the database with the user name and password specified in the arguments.
The default settings are as follows:

> この関数は引数で指定したユーザ名とパスワードでデータベースを構築します。
> デフォルトでは、以下のとおりに設定されています。

| Property | Value     |
|:---------|:----------|
| user     | admin     |
| password | p@ssw0rd  |
| dbname   | roadnetdb |
| port     | 5432      |

Road network calculation requires PostgreSQL extensions PostGIS and pgRouting.
Each extension can be enabled as follows.
You can also use the database without enabling these extensions.

> 道路ネットワークの計算には、PostgreSQLの拡張機能であるPostGISとpgRoutingが必要です。
> それぞれの拡張機能は次のようにして有効化できます。
> なお、これらを有効化せずに通常のデータベースとして利用することもできます。


```{r enable_extension, eval=FALSE}
enable_postgis()
enable_pgrouting()
```
